% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{CPD Report}

% Please do not change the subtitle
\subtitle{COMP330 - CPD Report}

% Please put your student number in the author field
\author{1605240}

\begin{document}

\maketitle

\section*{Introduction}
This term marks the penultimate term of university, scary to thing how fast time flies, therefore it is time for another CPD report. I have written brief descriptions of what I did every week and the main struggles I have faced throughout the term. In this report I identify my five key struggles and try to find ways I can improve on them and track my progress on them. This should help me in my final term of university and in the future.


\section{Time Management}
I believe time management is one of mans biggest downfalls if it is not done properly and unfortunately I fall into this category. This term I made progress on my work earlier on which I was very proud about, but I didn't split my time up equally between different modules, this is something I really struggle with because I think some modules require more effort than others. This is not always the case as some can turn out harder than expected and that's when you're in trouble. In industry if I fell behind in one aspect I'd get into trouble and would let my team down, in an extreme case I could end up losing my job. Since it's the start of a new year I've decided to get myself a diary to try and actively split my time fairly. To keep track of this I'll write down the hours I spend on each module per week and adjust so it's as equal as I need it to be.


\section{Sticking to my Tasks}
Sticking to my task is a struggle for me, I seem to always end up researching too far into the task and looking at the next step which can cause a lot of frustration or looking for similar tasks to do without completing the one I am working on. In the games industry I'd be tasked with completing one task to a basic level before improving it, I wouldn't be able to go off track or this could cause problems for the whole team. To ensure I stay on track I'm going to make more efficient use of Trello and break my tasks down into smaller ones and make sure I only complete what I am tasked with and nothing else. At the end of each week I will write down how many I complete and write down ones that weren't on the Trello and try get that number down to zero.


\section{Knowing When to Take a Break}
This term I especially struggled with knowing when to take a break, as silly as this sounds. I would work on a task, if I encountered a problem I would look for solutions and try for hours when it was such a simple problem that could have been solved just by taking a break and giving myself time to think. Doing this caused me to put myself under copious amounts of anxiety and stress, two things which I have great issues dealing with. In relation to the games industry like many of my other flaws, would lead to me slowing down team progress and eventually getting into more serious trouble. To try and improve this I will break after a certain time of being stuck to refresh, this is something that is hard to measure.


\section{Version Control}
My use of verion control has never been the best or most optimal way of doing things, we are always told to use GitHub to store our work. I however have just been copying and pasting the file to ensure I have a copy if need be. In industry I would not get away with this especially if someone else needed the file because they would have to come to me directly for a file. This isn't good as multiple people couldn't work on different branches because there are none. I need to start uploading all my work to GitHub every opportunity I get. To make sure I try and stick to my goal of getting this done I'm going to make sure every time I do work on a module once I am done the first thing I am going to do is upload it to GitHub and to measure I will see if my commits go up.

\section{Attendance}
My attendance has been the lowest it's ever been this term. I have been struggling with some mental health issues, although I should have gone to someone for help I did not. This is the first thing I am doing when I get back to university. I believe these issues have had such a large affect on the quality on a large percentage of the work I have submitted, I need to get help for the ASAP. In industry I could go and seek help and get some time off work if needed but couldn't just not show up for work with no excuse, this would just lead to me being sacked. To measure if my attendance has improved I will compare it to last term and see if it goes up and try to make myself go to university at least four days out of the week.

\section*{Conclusion}
Doing this report has helped me to identify the five main key skills that I am currently struggling with. If I follow all the guidelines I have set for myself it should help me lead to being a better university student as well as a better person. Sticking to goals is always a difficult task but I am determined to stick to them because that's the point of doing this. I am hoping to fix most of these goals out very quickly although one may take a little longer to fix than the others. I am still trying to to stick to the tasks set in all my pervious other CPD reports so adding to this should be a challenge. I like challenges.


\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}